Independent Component Analysis

### 2022-05-02 paper.tex
edited the boldface style in equations

J(Y) \propto \{E[G(Y)] - E[G(V)]\}^2,

@@

We want to find the extrema of $E[G(Y)]$ to maximize $J(Y)$ under the constraints

@@

E[(w^T x)^2] = \| w\|^2 = 1.

@@

E[x g(w^Tx)] - \beta w &= 0.

@@

Let $F(w)$ denote the left-hand side of the equation, which we are trying to solve.
We update the value of $w$ in each iteration according to the following equation.

@@

w_{n+1} &= w_n - \frac{F(w_n)}{F^{\prime}(w_n)} \\
&= w_n - \frac{E[x g (w_n^T x)] - \beta w_n}{E[g^{\prime}(w_n^T x)] - \beta} \\
&= \frac{w_n E[g^{\prime}(w_n^T x)] - \beta w_n - E[x g (w_n^T x)] + \beta w_n}{E[g^{\prime}(w_n^T x)] - \beta} \\
&= \frac{w_n E[g^{\prime}(w_n^T x)] - E[x g (w_n^T x)]}{E[g^{\prime}(w_n^T x)] - \beta}.

@@

A &= \begin{bmatrix}

>>>>

J(Y) \propto \{\mathbb{E}[G(Y)] - \mathbb{E}[G(V)]\}^2,

@@

We want to find the extrema of $\mathbb{E}[G(Y)]$ to maximize $J(Y)$ under the constraints

@@

\mathbb{E}(\mathbf{w}^{t}\mathbf{x})^2] = \| \mathbf{w}\|^2 = 1.

@@

\mathbb{E}[\mathbf{x}g(\mathbf{w}^{t}\mathbf{x})^2)] - \beta\mathbf{w} &= \mathbf{0}.

@@

Let $\mathbf{F}(\mathbf{w})$ denote the left-hand side of the equation, which we are trying to solve.
We update the value of $\mathbf{w}$ in each iteration according to the following equation.

@@

\mathbf{w}_{n+1} &= \mathbf{w}_n - \frac{\mathbf{F}(\mathbf{w}_n)}{F^{\prime}(\mathbf{w}_n)} \\
&= \mathbf{w}_n - \frac{\mathbb{E}[\mathbf{x}g(\mathbf{w}_n^t\mathbf{x})] - \beta \mathbf{w}_n}{\mathbb{E}[g^{\prime}(\mathbf{w}_n^t\mathbf{x})] - \beta} \\
&= \frac{\mathbf{w}_n\mathbb{E}[g^{\prime}(\mathbf{w}_n^t\mathbf{x})] - \beta\mathbf{w}_n - \mathbb{E}[\mathbf{x}g(\mathbf{w}_n^t\mathbf{x})] + \beta\mathbf{w}_n}{\mathbb{E}[g^{\prime}(\mathbf{w}_n^t\mathbf{x})] - \beta} \\
&= \frac{\mathbf{w}_n\mathbb{E}[g^{\prime}(\mathbf{w}_n^t\mathbf{x})] - \mathbb{E}[\mathbf{x}g(\mathbf{w}_n^t\mathbf{x})]}{\mathbb{E}[g^{\prime}(\mathbf{w}_n^t\mathbf{x})] - \beta}.

@@

\mathbf{A} &= \begin{bmatrix}
